Impact of Demographics and Skills of the Observer on Visual Statistical Inference

### 2013-02-26 sociology_paper.tex
update
discussion of visual test statistic

@@

\subsection{Choice of Visual Test Statistic} Discuss the effective feature of visual test statistics \citep{heike:2012}. Present some related results from \textit{Distance measure} of visual test statistics \citep{niladri:2012}.
\subsection{Question that Human Observer Faces} Discuss the importance of the question the observer needs to answer while evaluating the lineup.
\subsection{Observer Personality}
\subsection{Visual Perception of Human Eye} Discuss the results we have on eye tracking experiment \citep{zhao:2012}.
\subsection{Demographics of Observer}  Age, gender and location of the observer.
\subsection{Skills of Observer} Knowledge about statistical plot as well as education level.

@@

\subsection{Experiment Setup} Description of the simulation experiment giving focus on demographics and skills of experimental subjects.
\subsection{Diversity of the Experimental Subjects} Discuss why it would be important and how we accomplish this using Amazon Mechanical Turk \cite{turk} web site.

\section{Results}
\subsection{Overview of the Data}
\subsection{Learning Trend of the Observer} Since each subject is shown multiple lineups, they have a chance for self learning and do better on lineups shown later in the sequence. We examine this by fitting generalized mixed effect model presented in \cite{majumder:2012} with covariates attempt number and $p$-value of the lineup. The $p$-value of the lineup measures some sort of difficulty and including this should adjust for the difficulty level of the lineup while estimating the probability of correct responses in each attempt. Figure \ref{fig:learning_trend} shows the fitted subject wise learning pattern as well as overall learning pattern for each of the experiments. The parameter estimates od the model are shown in Table \ref{tbl:model_par}.

>>>>

\tableofcontents

@@

\subsection{Choice of Visual Test Statistic} Visual test statistics as defined in \citep{majumder:2012} serve two main purposes. One is to display a prominent pattern that should direct the human observers to select the actual plot in the lineup when the null hypothesis is not true. The another feature is that it should not show any strange pattern when null hypothesis is true, i.e., it should show similar pattern that null plots may have. Thus a visual test statistic is highly associated with the hypothesis. To achieve these purposes it is very important to decide which plot type and plot features should be adopted. As discussed in \citep{majumder:2012} following grammar of graphics developed  by \citet{wilkinson:1999} and later improved by \citet{hadley:2009} can give the task a standard control.

Some of the effective features of visual test statistics are discussed in \citep{heike:2012} including plot type, color and shape of the plots. It is also observed that a scatterplot may do a better job than a box plot when using as a visual test statistic for regression parameters \citep{majumder:2012} .  \citep{niladri:2012} presents some \textit{distance measure} to determine how a plot may be different from another.

Plots to do: for the same signal strength show the proportion correct for scatterplot and boxplot. eg., qplot(effect, ump-visual power, color= plot-type)

\subsection{Question that Human Observer Faces} Discuss the importance of the question the observer needs to answer while evaluating the lineup.
\subsection{Observer Personality}
\subsection{Visual Perception of Human Eye} Discuss the results we have on eye tracking experiment \citep{zhao:2012}.
\subsection{Demographics of Observer}  Age, gender and location of the observer.
\subsection{Skills of Observer} Knowledge about statistical plot as well as education level.

@@

\subsection{Experiment Setup} Description of the simulation experiment giving focus on demographics and skills of experimental subjects.
\subsection{Estimation of sample size}  How the sample size is estimated
\subsection{Data collection methods}  Description of the simulation experiment giving focus on demographics and skills of experimental subjects.

\section{Results}
\subsection{Overview of the Data}
\subsection{Diversity of the Experimental Subjects} Amazon Mechanical Turk \cite{turk} web site is a good source for recruiting people to evaluation lineups. It is a source of diverse workers who can give us feedback on visual inspection. This is the kind of task where human are better than computers.  Figure \ref{} shows the location from where we received data. Notice that we received data from around the world and we observed diversity of location in the collected data. We notice diversity in not only location of the observers but also their gender, age groups and education levels. Table \ref{} shows that we have data from almost similar size of male and female population.

\subsection{Learning Trend of the Observer} Since each subject is shown multiple lineups, they have a chance for self learning and do better on lineups shown later in the sequence. We examine this by fitting generalized mixed effect model presented in \cite{majumder:2012} with covariates attempt number and $p$-value of the lineup. The $p$-value of the lineup measures some sort of difficulty and including this should adjust for the difficulty level of the lineup while estimating the probability of correct responses in each attempt. Figure \ref{fig:learning_trend} shows the fitted subject wise learning pattern as well as overall learning pattern for each of the experiments. The parameter estimates od the model are shown in Table \ref{tbl:model_par}.
